DOpElib - Deal Optimization Environment

### 2012-09-06 Examples/PDE/InstatPDE/Example1/content.tex
Docu of PDE/InstatPDE/Example1 has some flaws.

\subsubsection{General problem description}
In this example we consider the nonstationary incompressible Stokes equation. As in the stationary PDE Example 3 \ref{PDE_Stat_FSI_STVK},
we use the symmetric fluid stress tensor.  
In strong formulation we deal with 
\begin{align*}
\partial_t v -\nabla\cdot (\nabla v + \nabla v^{T}) + \nabla p &= f \\
div\, v &= 0 
\end{align*}
on time interval $I=[0,T]$ and the domain 
$\Omega = [-6,6]\times [0,2]$. For simplicity,  we set $f=0$.

@@

However, solving the Navier-Stokes equations are 
multi-physics problems (like fluid-structure
interaction), parts of the equations are treated
with a fully implicit time-stepping scheme.

>>>>

\subsubsection{General problem description}
In this example we consider the nonstationary incompressible Navier-Stokes equation. As in the stationary PDE Example 3 \ref{PDE_Stat_FSI_STVK},
we use the symmetric fluid stress tensor.

\textbf{The rest of this parte is written for Stokes instead of Navier-Stokes. Needs to be adjusted.}

In strong formulation we deal with 
\begin{align*}
\partial_t v -\nabla\cdot (\nabla v + \nabla v^{T}) + \nabla p &= f \\
div\, v &= 0 
\end{align*}
on time interval $I=[0,T]$ and the domain 
$\Omega = [-6,6]\times [0,2]$. For simplicity,  we set $f=0$.

@@

However, solving the Navier-Stokes equations or 
multi-physics problems (like fluid-structure
interaction), parts of the equations are treated
with a fully implicit time-stepping scheme.
